The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

>>>>

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” (Freytag Andreas, Thurik Roy, 2007). Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others. Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report 2009).

Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out. It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund (Davidsson and Wiklund study 1997), at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure, and observed different outcomes, they concluded on the possibility of a small cultural effect.

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
